LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-12-08 main.tex
Remove stray draft options
List demo runtimes

\documentclass[draft]{article}

\usepackage{amsmath}
\usepackage[uniquename=init,firstinits,backend=biber,sorting=none]{biblatex}
\usepackage{commath}
\usepackage{fontspec}
\usepackage{gensymb}
\usepackage{import}
\usepackage[final]{listings}
\usepackage[numbered,framed]{mcode}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

@@

This section presents the use of LCS Tool in three examples: a double gyre, a jet, and an oceanic geostrophic flow. The examples are available as scripts in the demo folder of LCS Tool. Executing these scripts can help readers follow LCS Tool computations.

% FIXME Performance also described in Conclusions section
The scripts call LCS Tool functions.
These functions are written to achieve balance between ease of use and performance.
% FIXME With lambda range demo runtimes can be over an hour.
% FIXME List runtime of demo scripts in a table
Running the demo scripts takes on the order of minutes.

>>>>

\documentclass{article}

\usepackage{amsmath}
\usepackage[uniquename=init,firstinits,backend=biber,sorting=none]{biblatex}
\usepackage{commath}
\usepackage{fontspec}
\usepackage{gensymb}
\usepackage{import}
\usepackage{listings}
\usepackage[numbered,framed]{mcode}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}

@@

This section presents the use of LCS Tool in three examples: a double gyre, a jet, and an oceanic geostrophic flow.
The examples are available as scripts in the demo folder of LCS Tool.
Executing these scripts demonstrates how to call LCS Tool functions.
These functions are written to achieve balance between ease of use and performance.
Examples of demo runtimes are given in \cref{t:demo runtimes}.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Demo & Runtime (min)\tabularnewline
\hline \hline
double\_gyre/elliptic\_hyperbolic\_lcs & 50\tabularnewline
\hline
bickley\_jet/elliptic\_hyperbolic\_lcs\_details & 975\tabularnewline
\hline
ocean\_dataset/elliptic\_hyperbolic\_lcs\_details & 127\tabularnewline
\hline
\end{tabular}
\end{center}
\caption{Runtime of some demo scripts Results obtained with an Intel Core i3-4130 processor with eight gigabytes of memory.}
\label{t:demo runtimes}
\end{table}
